---
title: ""
subtitle: ""
author: "Lars Schöbitz"
date: "2021-03-03"
output:
  xaringan::moon_reader:
    css: ["default", "assets/css/my-css-style.css", "assets/css/xaringan-themer.css"]
    seal: false 
    lib_dir: libs
    nature:
      slideNumberFormat: |
        <div class="progress-bar-container">
          <div class="progress-bar" style="width: calc(%current% / %total% * 100%);">
          </div>
        </div>
      highlightStyle: solarized-light
      highlightLanguage: ["r", "css", "yaml"]
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
---

```{r setup, include=FALSE}
options(
  htmltools.dir.version = FALSE,   
  htmltools.preserve.raw = FALSE # to fix HTML issue
  )
knitr::opts_chunk$set(collapse = TRUE,
                      fig.retina = 3)
library(tidyverse)
library(xaringanExtra)
xaringanExtra::use_panelset()
xaringanExtra::use_share_again()
xaringanExtra::style_share_again(
  share_buttons = c("twitter", "linkedin", "pocket")
)

# load packages -----------------------------------------------------------

library(xaringanthemer)

# set options -------------------------------------------------------------

style_mono_accent(
  base_color = "#0F4C81", # Pantone Classic Blue
  header_font_google = google_font("Montserrat"),
  code_font_google = google_font("Fira Mono"), 
  code_font_size = "1.2rem",
  text_font_size = "1.4rem", 
  header_h1_font_size = "2.0rem",
  header_h2_font_size = "1.75rem",
  header_h3_font_size = "1.5rem",
  footnote_font_size = "0.8rem",
  footnote_position_bottom = "20px",
  header_background_padding = "2rem",
  outfile = here::here("slides/assets/css/xaringan-themer.css")
)

# htmttools

library(htmltools)

```

```{r broadcast, echo=FALSE}
xaringanExtra::use_broadcast()
```

class: title-slide

<script async defer data-domain="lse.de" src="https://plausible.io/js/plausible.js"></script>


# `r rmarkdown::metadata$title`

## `r rmarkdown::metadata$subtitle`

.bottom[

```{r, echo=FALSE}
p(rmarkdown::metadata$author)
p(rmarkdown::metadata$date)
```
]

???

---
layout: true


---
class: middle

# .big[Welcome! `r emo::ji("wave")`]

---
# 

---
# `r emo::ji("sunflower")` Thank you!
***

For stopping by.

For R packages [{xaringan}](https://github.com/yihui/xaringan) and [{xaringanthemer}](https://github.com/gadenbuie/xaringanthemer), which where used to create these slides.

All material is licensed under [Creative Commons Attribution Share Alike 4.0 International](https://creativecommons.org/licenses/by-sa/4.0/). To download a PDF version of these slides [click here](https://github.com/larnsce/co-wash-symposium-2021/raw/main/docs/slides/co-wash-symposium-data-science-for-wash-slides.pdf).


---
class: center

.big[➡️ kutt.it/cowash2021 ⬅️]   

--
`r emo::ji("index_pointing_up_medium_dark_skin_tone")` Register for Colorado WASH Sympsoium 2021  

--
`r emo::ji("victory_hand_medium_skin_tone")` Create a free account on RStudio Cloud  

--
`r emo::ji("OK_hand_medium_dark_skin_tone")` Read the Code of Conduct for this workshop
